From Reversible Programs to \\ Univalent Universes and Back

### 2021-10-27 Pi/paper/finite.tex
Restore some HoTT text from appendix
Fixes #141
Expand homotopy types and add fib/im
Fixes #149
Fix broken references

Despite the increased complexity of the generators, the rewriting system $(\List[\Fin[n]],\longcox)$ has the properties
we desire. It satisfies local confluence, that is, the Church-Rosser (diamond) property -- for example, using
$\longbraid$, we can now show the problematic critical pair \cref{fig:critical-pairs-non-converging} converges, and, it
is terminating, so by Newman's lemma, it produces a unique normal form. We follow the terminology
of~\citet*{huetConfluentReductionsAbstract1980a,krausCoherenceWellFoundednessTaming2020} to state our results formally.

@@

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item $\normf$ splits into a section-retraction pair, that is, we have ${\List[\Fin[n]]} \xrightarrow{s} \Sn[n]
            \xrightarrow{r} {\List[\Fin[n]]}$ such that $s \comp r \htpy \normf$ and $r \comp s \htpy \idfunc_{\Sn[n]}$.
    \item \(\im{\quotinc} \eqv \Sn \eqv \im{\normf} \), where $\quotinc$ is the mapping into the quotient, and
          $\im{f}$ denotes the image of $f$ (see~\cref{def:im}).
  \end{enumerate}
\end{proposition}

@@

\begin{theoremrep}
  \leavevmode
  \begin{enumerate}
    \item For any Lehmer code $c$, $\immersion_{n}(c)$ is a normal form with respect to $\longcoxstar$, that is,
          $\immersion_{n}(c)$ is in $\im{\normf}$.
    \item Any element of $\im{\normf}$ can be constructed from a unique Lehmer code by $\immersion$, that is, the fibers
          of $\immersion_{n} : \Lehmer[n] \to {\im{\normf}}$ are contractible.
  \end{enumerate}
  Therefore, there is an equivalence between $\Lehmer[n]$ and $\im{\normf}$.
\end{theoremrep}

>>>>

Despite the increased complexity of the generators, the rewriting system $(\List[\Fin[n]],\longcox)$ has the properties
we desire. It satisfies local confluence, that is, the Church-Rosser (diamond) property -- for example, using
$\longbraid$, we can now show the problematic critical pair \cref{fig:critical-pairs-non-converging} converges, and, it
is terminating, so by Newman's lemma, it produces a unique normal form. We follow the terminology
of~\citet*{huetConfluentReductionsAbstract1980,krausCoherenceWellFoundednessTaming2020} to state our results formally.

@@

\begin{proposition}
  \leavevmode
  \begin{enumerate}
    \item $\normf$ splits into a section-retraction pair, that is, we have ${\List[\Fin[n]]} \xrightarrow{s} \Sn[n]
            \xrightarrow{r} {\List[\Fin[n]]}$ such that $s \comp r \htpy \normf$ and $r \comp s \htpy \idfunc_{\Sn[n]}$.
    \item \(\im{\quotinc} \eqv \Sn \eqv \im{\normf} \), where $\quotinc : \List[\Fin[n]] \to \Sn$ is the mapping into
    the quotient.
  \end{enumerate}
\end{proposition}

@@

\begin{theoremrep}
  \leavevmode
  \begin{enumerate}
    \item For any Lehmer code $c$, $\immersion_{n}(c)$ is a normal form with respect to $\longcoxstar$, that is,
          $\immersion_{n}(c)$ is in $\im{\normf}$.
    \item Any element of $\im{\normf}$ can be constructed from a unique Lehmer code by $\immersion$, that is, the fibers
          of $\immersion_{n} : \Lehmer[n] \to {\im{\normf}}$ are contractible.
  \end{enumerate}
  Therefore, there is an equivalence between $\Lehmer[n]$ and $\im{\normf}$ (see~\cref{prop:three-chars-equiv}).
\end{theoremrep}
